Manuscript title here

### 2021-05-31 doc/ms/ms.Rmd
update writing.

We compared the empirical $Sk_{flux}$ measurement within streams to a random ordering to detect random vs. non-random structure in the community energy fluxes. the probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`. Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% min%>% round(2)` to `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% max%>% round(2)`. The probability that

@@

# Discussion

>>>>

We compared the empirical $Sk_{flux}$ measurement within streams to a random ordering to detect random vs. non-random structure in the community energy fluxes. The probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`. Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% min%>% round(2)` to `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% max%>% round(2)`. The probability that

@@

#Discussion

Changing global temperatures are altering the pathways of energy flow across and within ecosystems. Here, we document shifting energy flow pathways across a wide natural temperature gradient, wherein, increasing mean annual temperatures are associated with reductions in mean community body size and a concomitant increase in population biomass turnover. Further,
